intro

### 2021-11-10 06_Paper/ER-ED/intro.Rmd
Added two intro sentences
added intro sentences
Added sentence Added comments for structuring

<!-- Einführung ER -->
[...]
Implications of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
For example, it could be shown that maladaptive ER strategies mediate the effect between Neurotizism and depressive symptoms [@Yoon2013].
Also, meta-analytic evidence exists linking a number of ER strategies with psychological disorders [@Aldao2010].
The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
First, adaptive flexible ER requires having a large repertoire of ER strategies [@Aldao2015]. 
For example, greater ER variability is related to reduced negative affect and therefore adaptive in daily life [@Blanke2020].
Second, strategies have to be chosen from the repertoire that are useful for goal achieving.
This selection of strategies is influenced by numerous factors.
For example, it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction[@Sheppes2011;@Sheppes2014].
Further influencing factors are for example extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
Especially for effort, Scheffel and colleagues [-@Scheffel2021] could show that the choice for an ER strategy is mainly influenced by effort.
In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards they could choose, which strategy they want to use again.
Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one - in this case: suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.

>>>>

Every day we are confronted with stressful or emotionally demanding situations. 
The ability to modify emotional experiences, expressions and physiology [@Gross1998antecedent] regulate emotions is an important cognitive skill. 
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].

<!-- Nun ER Strategies aufzählen -->
<!-- Wirksamkeit von ER Strategien -> Meta Analyse Webb -->
<!-- Evtl noch auf einzelne Strategien eingehen (Distancing, Distraction, Suppression) -->
[...]
Implications of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
For example, it could be shown that maladaptive ER strategies mediate the effect between Neurotizism and depressive symptoms [@Yoon2013].
Also, meta-analytic evidence exists linking a number of ER strategies with psychological disorders [@Aldao2010].
The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
First, adaptive flexible ER requires having a large repertoire of ER strategies [@Aldao2015]. 
For example, greater ER variability is related to reduced negative affect and therefore adaptive in daily life [@Blanke2020].
Second, strategies have to be chosen from the repertoire that are useful for goal achieving.
This selection of strategies is influenced by numerous factors.
For example, it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction[@Sheppes2011;@Sheppes2014].
Further influencing factors are for example extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
Especially for effort, Scheffel and colleagues [-@Scheffel2021] could show that the choice for an ER strategy is mainly influenced by effort.
In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards they could choose, which strategy they want to use again.
Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one - in this case: suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
